---
graphics: yes
name: Chris
surname: Guiterman
given-name-pattern: Christopher
family-name-pattern: Guiterman
headcolor: 00008B
# position: "Research Scientist"
address: "Laboratory of Tree-Ring Research, University of Arizona \\tabularnewline Permanent residence: Hanover, New Hampshire \\tabularnewline"
phone: +1 781-296-3667
www: chris-guiterman.rbind.io
email: chguiterman@arizona.edu
twitter: ChrisGuiterman
github: chguiterman
aboutme: |
 Forest and fire ecology | Climate change | Coupled human-natural systems | Applications in dendrochronology
date: "`r format(Sys.time(), '%B %Y')`"
csl: "../csl/apa6-cv.csl"
nocite: "@*"
knit: bookdown::render_book
bibliography_journals: "../data/Journal_publications2.bib"
bibliography_inreview: "../data/Journal_inReview.bib"
bibliography_inprep: "../data/Journal_inPrep.bib"
bibliography_reports: "../data/Other_pubs.bib"

---

```{r eval=FALSE, include=FALSE}
# Remember to spell check!!
# data_files <- list.files(here::here("data"), pattern = ".csv", full.names = TRUE)
# spelling::spell_check_files(c("CV.Rmd", data_files))
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(lubridate)
library(here)
library(readxl)
library(glue)
library(conflicted)
library(scales)
conflict_prefer("filter", "dplyr")
conflict_prefer("here", "here")
```

<!--chapter:end:CV_teaching.Rmd-->

# Education

```{r edu}
edu.raw <- read_csv(here("data", "education.csv"))
edu <-
  edu.raw %>% 
  mutate(chair = glue("Chair: {chair}"),
         dissertation = glue("\\textbf{[dissertation]}", 
                             .open = "[", .close = "]")
         ) %>% 
  gather(dissertation, chair, key = "whytype", value = "why")

edu %>%
  filter(whytype == "dissertation") %>%
  brief_entries(when = end_date,
                what = degree,
                with = glue("{university}, {department}, {location}"),
                .protect = FALSE)

```

<!--chapter:end:../education.Rmd-->

# Work Experience

```{r jobs}
jobs <- read_csv(here("data", "jobs.csv")) %>% 
   filter(!is.na(start_date)) %>% 
   mutate(Start = mdy(start_date),
         End = mdy(end_date)) %>% 
  mutate(When = case_when(
    is.na(End) ~ glue("{year(Start)}--    ") %>% as.character(),
    year(Start) == year(End) ~ year(End) %>% as.character(),
    TRUE ~ glue("{year(Start)}--{year(End)}") %>% as.character()
  )) %>% 
  mutate(End = if_else(is.na(End), today() + years(2), End)) #if no end date specified, set it to two years from now for sorting purposes, i.e. so jobs I'm still doing show up at top

jobs %>% 
  select(-why) %>% 
  arrange(desc(End)) %>% 
  # filter(where != "Joseph, OR") %>% 
  brief_entries(
    what = what,
    when = When,
    with = glue("{with}, {where}"),
    .protect = FALSE
  )

```

<!--chapter:end:../work.Rmd-->


# Teaching Experience
## Lead or co-instructor

```{r teaching}
courses <- read.csv(here("data", "teaching.csv")) %>% 
  mutate(when = glue("{semester} {year}")) %>% 
  arrange(desc(year))

courses %>% 
  filter(tag == "Instructor") %>% 
  detailed_entries(
    when = when,
    what = what,
    with = glue("{with}, {where}"),
    why = glue("{description}"),
    .protect = FALSE
  )
```
## Teaching assistant
```{r}
courses %>% 
  filter(tag == "TA") %>% 
  brief_entries(
    when = when,
    what = what,
    with = glue("{with}, {where}"),
    .protect = FALSE
  )
```

<!--chapter:end:teaching_teaching.Rmd-->


# Grants & Fellowships

```{r grants data}
grants <- read_csv(here("data", "grants.csv")) %>% 
  mutate(date = case_when(
    is.na(start_year) ~ glue("{end_year}"),
    TRUE ~ glue("{start_year}--{end_year}")
  )
  ) %>% 
  arrange(desc(end_year))
```

Total research funding: `r dollar(sum(grants$amount, na.rm=TRUE) - 500)`

*Note: I served as the project lead and/or PI unless otherwise specified*

\vspace{12pt}

```{r submitted grants}
sub_gr <- tribble(~ date, ~ title, ~ sponsor, ~ amount, ~ collab,
                  "Submitted", "Feedbacks and scale at an ancient wildland-urban interface", "NSF Dynamics of Integrated Socio-Environmental Systems", 1599949, "Chris Roos (PI). UofA (Guiterman co-PI) share $362,117.",
                  "Invited, second round", "rIMPD: The North American tree-ring fire history database in R", "USGS Community for Data Integration", 50000, "Ellis Margolis"
)

sub_gr %>% 
    detailed_entries(
    when = date, 
    what = title,
    with = sponsor, 
    where = dollar(amount),
    # why =  ifelse(!is.na(PI), glue("{PI} (PI)"), NA)
    why = ifelse(!is.na(collab), glue("with {collab}"), NA)
  )

```

```{r awarded grants}
grants %>% 
  detailed_entries(
    when = date, 
    what = title,
    with = sponsor, 
    where = dollar(amount),
    # why =  ifelse(!is.na(PI), glue("{PI} (PI)"), NA)
    why = ifelse(!is.na(collab), glue("with {collab}"), NA)
  )
```

<!--chapter:end:../grants.Rmd-->

# Awards & Honors
```{r awards}
awards <- read.csv(here("data", "awards.csv")) %>% 
  arrange(desc(when))
awards %>% 
  brief_entries(when = when,
                what = what,
                with = where)
```

<!--chapter:end:../awards.Rmd-->

# Publications

<!-- ## Selected Publications

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_selected}
:::
\endgroup -->

## Refereed Journal Papers

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{1.0in}
\setlength{\parskip}{8pt}

::: {#refs_journals}
:::
\endgroup

\vspace{12pt}

## Papers in review

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{1.0in}
\setlength{\parskip}{8pt}

::: {#refs_inreview}
:::
\endgroup

\vspace{12pt}

## Papers in preparation

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{1.0in}
\setlength{\parskip}{8pt}

::: {#refs_inprep}
:::
\endgroup

\vspace{12pt}

## Other publications and reports

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{1.0in}
\setlength{\parskip}{8pt}

::: {#refs_reports}
:::
\endgroup

\vspace{12pt}

## Software
```{r}
df <- tribble(~what, ~when, ~with, ~where, ~why,
              "dfoliatR: detection and analysis of insect defoliation signals in tree rings", 2020, "CH Guiterman, AM Lynch, JN Axelson",
              "https://chguiterman.github.io/dfoliatR/", "Author, Creator, Maintainer",
              "burnr: Advanced fire history tools in R", 2016, 
              "SB Malevich, CH Guiterman, EQ Margolis",
              "https://cran.r-project.org/web/packages/burnr/index.html",
              "Author, Contributor",
              "suRge: An extension of dfoliatR to accomodate insect-induced growth surges in trees", 2019, "developed for Amy Hessl (West Virginia University)", "https://github.com/chguiterman/suRge", "Author, Creator",
              "slideRun: An extension of burnr to assess avalanche damage patterns on trees", 2018, "developed for Erich Peitzsch and Greg Pederson (USGS Montana)",
              "https://github.com/chguiterman/slideRun", "Author, Creator",
              "burnr_demo: A module-based R project for educating burnr users", 2017, "CH Guiterman", "https://github.com/chguiterman/burnr_demo", "Author, Creator"
)
df %>% 
  detailed_entries(what = what, 
                   when = when, 
                   with = with, 
                   where = where, 
                   why = NULL)

```

<!--chapter:end:../publication.Rmd-->


# Service

\begingroup
\setlength{\leftskip}{0.5in}

**Journal peer reviews:** *Dendrochronologia,
Fire Ecology,
Forest Ecology and Management,
Forest Science,
Global Ecology and Biogeography,
Geophysical Research Letters,
International Journal of Wildland Fire,
Journal of Archaeological Method and Theory,
Journal of Biogeography,
Journal of Contemporary Water Research and Education,
Journal of Hydrology,
Journal of Vegetation Science,
Tree-Ring Research,
Urban Forestry and Urban Greening*

\endgroup

\vspace{12pt}

```{r}
serv <- read.csv(here("data", "service.csv")) 
serv %>% 
  arrange(desc(when)) %>% 
  detailed_entries(when = when,
                   what = what,
                   where = where)
```

<!--chapter:end:../service.Rmd-->


# Presentations

## Invited seminars
```{r presentations}
 presentations <- read_csv(here("data", "presentations.csv")) %>%  
   mutate(When = mdy(When)) 

presentations %>% 
  filter(Tag == "seminar") %>% 
  arrange(desc(When)) %>% 
  detailed_entries(what = Title,
                   when = glue("{month(When, label = TRUE)} {year(When)}"),
                   where = glue("{Conference}, {Location}"), 
                   .protect = TRUE)
```

## Conference presentations  (last five years)

```{r}
presentations %>%
  filter(Tag %in% c("talk", "invited")) %>%
  arrange(desc(When)) %>%
  detailed_entries(what = Title,
                   when = glue("{month(When, label = TRUE)} {year(When)}"),
                   with = Authors,
                   where = glue("{Conference}, {Location}"), 
                   why = Why, 
                   .protect = FALSE)
```

<!-- ## Conference posters (last five years) -->
<!-- ``` {r} -->
<!-- presentations %>% -->
<!--   filter(Tag == "poster") %>% -->
<!--   arrange(desc(When)) %>% -->
<!--   detailed_entries(what = Title, -->
<!--                    when = glue("{month(When, label = TRUE)} {year(When)}"), -->
<!--                    with = Authors, -->
<!--                    where = glue("{Conference}, {Location}"),  -->
<!--                    why = Why,  -->
<!--                    .protect = FALSE) -->
<!-- ```                    -->

<!--chapter:end:../presentations.Rmd-->

# Professional Society Memberships

|           * Tree-Ring Society
|           * Forest Stewards Guild
|           * Society of American Foresters
|           * Association for Fire Ecology
|           * Association of American Geographers
|           * Society of American Archaeology
  
\vspace{12pt}

<!--chapter:end:../memberships.Rmd-->

# Student Research Assistants & Mentees

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{1.0in}
<!-- \setlength{\parskip}{8pt} -->

**Eze Ahanonu**, undergraduate, field and lab (2014-2016)

**Royale Billy-Wilson**, undergraduate, field and lab (2015-2017)

**Patrick Brewer**, undergraduate, field and lab (2015-2016)


**Alec Gagliano**, undergraduate, field and lab (2016-2018)

**Galen Gudenkauf**, undergraduate, field (2014)

**Jordan Krcmaric**, post-graduate, field (2017)

**Ben Olimpio**, undergraduate, lab (2016-2017)

**Anna Penaloza**, undergraduate, lab (2013)

**Gabryl Sam**, post-graduate, field (2019)

**Melissa Schwan**, undergraduate and post-graduate, field and lab (2015-2018)

**Eric Shreve**, undergraduate, lab (2012-2013)

**Jaime Yazzie**, post-graduate, field (2019)


\endgroup

\vspace{12pt}

<!--chapter:end:../lab_group.Rmd-->

